Additional analyses

### 2023-11-28 procesamiento/prod_analysis-plots-models.Rmd
ajustes PAC

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(theme_bw())
ggplot2::theme_update(text=element_text(size=15,  family="serif"))  
```

@@

df_p_full<- 
bind_rows(
  fsample_egal_full_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Full network"),
  fsample_egal_strong_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Strong ties"),
  fsample_egal_weak_ind[[3]] %>%
    broom.mixed::tidy(conf.int = T) %>%
    filter(term %in% coef) %>%
    mutate(group ="Weak ties")
)
df_p_full$depvar <- "Full sample"
```

@@

ggplot(df_p,
       aes(x = estimate, y = term, color = group)) +
  geom_vline(xintercept = 0) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    size = 1,
    width = 0.2,
    position = position_dodge(0.5)
  ) +
  geom_point(
    shape = 21,
    size = 3,
    fill = "white",
    position = position_dodge(0.5)
  ) +
  facet_grid(~depvar)+
  scale_y_discrete(
    labels = c(
      "Working Class (VI+VII)",
      "Intermediate class (III+IV+V)",
      "Class-based homogeneity"
    )
  )+
  scale_color_discrete(guide = guide_legend(reverse = TRUE))+
  labs(
    # caption = paste0("N=", nobs(int_homo), ", Countries=", lme4::ngrps(int_homo)),
    color = "Model",
    x="Coefficients (fixed effects)",y=NULL,
    title = "Egalitarian Economic Preferences (Index)") +
  theme(axis.text.y.left = element_text(face = "plain", size = 12))

ggsave(plot = last_plot(),filename = "coefplot-egal.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)
```

>>>>

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(theme_minimal())
ggplot2::theme_update(text=element_text(size=15,  family="serif"))  
```

@@

df_p_full<- 
bind_rows(
  fsample_egal_full_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Full network"),
  fsample_egal_strong_ind[[3]] %>% 
    broom.mixed::tidy(conf.int = T) %>% 
    filter(term %in% coef) %>% 
    mutate(group ="Strong ties"),
  fsample_egal_weak_ind[[3]] %>%
    broom.mixed::tidy(conf.int = T) %>%
    filter(term %in% coef) %>%
    mutate(group ="Weak ties")
)
df_p_full$depvar <- "Full sample"

```

@@

ggplot(df_p,
       aes(x = estimate, y = term, color = group)) +
  geom_vline(xintercept = 0) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    size = 1,
    width = 0.2,
    position = position_dodge(0.5)
  ) +
  geom_point(
    shape = 21,
    size = 3,
    fill = "white",
    position = position_dodge(0.5)
  ) +
  facet_grid(~depvar)+
  scale_y_discrete(
    labels = c(
      "Working Class (VI+VII)",
      "Intermediate class (III+IV+V)",
      "Class-based homogeneity"
    )
  )+
  scale_color_discrete(guide = guide_legend(reverse = TRUE))+
  labs(
    # caption = paste0("N=", nobs(int_homo), ", Countries=", lme4::ngrps(int_homo)),
    color = "Model",
    x="Coefficients (fixed effects)",y=NULL,
    title = "Redistributive Preferences (Index)") +
  theme(axis.text.y.left = element_text(face = "plain", size = 12))

ggsave(plot = last_plot(),filename = "coefplot-egal.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 15)

```

```{r coef-egal-fullsample}
ggplot(df_p %>% filter(depvar=="Full sample"),
       aes(x = estimate, y = term, color = group)) +
  geom_vline(xintercept = 0) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    size = 1,
    width = 0.2,
    position = position_dodge(0.5)
  ) +
  geom_point(
    shape = 21,
    size = 3,
    fill = "white",
    position = position_dodge(0.5)
  ) +
  facet_grid(~depvar)+
  scale_y_discrete(
    labels = c(
      "Working Class (VI+VII)",
      "Intermediate class (III+IV+V)",
      "Class-based homogeneity"
    )
  )+
  scale_color_discrete(guide = guide_legend(reverse = TRUE))+
  labs(
    # caption = paste0("N=", nobs(int_homo), ", Countries=", lme4::ngrps(int_homo)),
    color = "Model",
    x="Coefficients (fixed effects)",y=NULL,
    title = "Redistributive Preferences (Index)") +
  theme(axis.text.y.left = element_text(face = "plain", size = 12))
ggsave(plot = last_plot(),filename = "coefplot-egal-fullsample.png",device = "png",
       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 15)

```

```{r inter-egal-fnet-fsample}
int_homo <- fsample_egal_full_ind[[4]]
interplot <- 
interplot::interplot(m = int_homo,var1 = "homclass",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV+V)","Working Class (VI+VII)")
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (VI+VII)","Intermediate class (III+IV+V)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  ylab("Class-based homogeneity (Full ties)")+
  xlab("Social Class")+
  ggtitle("Redistributive preferences") +
  geom_hline(yintercept = 0) + 
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +    
  theme(plot.title = element_text(size = 15))

ggsave(plot = last_plot(),filename = "mar_homo_class.png",device = "png",
       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 15)

df_pred1 <- plot_predictions(int_homo, condition = c("homclass","class3"),draw = F) 
# names(df_pred1)
df_pred1 %>% 
ggplot(aes(y =estimate,x=homclass, fill=class3, color=class3,ymin=conf.low, ymax=conf.high)) +
  geom_line(size=0.75) +
  geom_point(size=1) +
  geom_ribbon(alpha=0.2,size=0.5,linetype=1) +
  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),c("Service Class (I+II)","Intermediate class (III+IV+V)","Working Class (VI+VII)"))) +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  xlab("Network homogeneity (Full ties)")+
  ylab("Redistributive preferences") +
  theme(legend.position = "none", legend.title = element_blank())

ggsave(plot = last_plot(),filename = "predict-egal-fullsample.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 14)
```

```{r inter-macro}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,gridExtra)       
rm(list=ls())
load(here::here("output/fullsample-egalitarian-homclass-full-macro.RData"));fsample_egal_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)

p1<- interplot::interplot(m = fsample_egal_full_mac[[1]],var1 = "homclass",var2="gini_disp",ci = .95)+
  ylab("Class-based homogeneity coefficient")+ xlab("Gini disposable") + 
  geom_point()+ geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "marginal-homoXginiD.png",device = "png",
       path = here::here("output/images"),width = 1.25,height = 1,units = "cm",scale = 14)

p2<- interplot::interplot(m = fsample_egal_full_mac[[2]],var1 = "homclass",var2="gini_mkt") +
  ylab("Class-based homogeneity coefficient")+ xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "marginal-homoXginiM.png",device = "png",
       path = here::here("output/images"),width = 1.25,height = 1,units = "cm",scale = 14)

# Predicted values 
predval1 <- 
plot_predictions(fsample_egal_full_mac[[1]], condition = list("homclass",gini_disp=range),gray = F) +
  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
       colour='Gini (Dis)',fill='Gini (Dis)') +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

ggsave(plot = last_plot(),filename = "predict-homoXginiD.png",device = "png",
       path = here::here("output/images"),width = 1.25,height = 1,units = "cm",scale = 14)

# Predicted values 
predval2 <- 
plot_predictions(fsample_egal_full_mac[[2]], condition = list("homclass",gini_mkt=range),gray = F) +
  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
       colour='Gini (Mkt)',fill='Gini (Mkt)') +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

ggsave(plot = last_plot(),filename = "predict-homoXginiM.png",device = "png",
       path = here::here("output/images"),width = 1.25,height = 1,units = "cm",scale = 14)

```

### 2023-11-28 procesamiento/prod_analysis-tables-macro.Rmd
ajustes PAC

htmlreg(
  c(fsample_num_full_mac,fsample_num_strong_mac,fsample_num_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

@@

htmlreg(
  c(fsample_egal_full_mac,fsample_egal_strong_mac,fsample_egal_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

>>>>

knitreg(
  c(fsample_num_full_mac,fsample_num_strong_mac,fsample_num_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

@@

knitreg(
  c(fsample_egal_full_mac,fsample_egal_strong_mac,fsample_egal_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

### 2023-11-28 procesamiento/prod_analysis-tables-micro.Rmd
ajustes PAC

htmlreg(
  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
  caption = "Multilevel linear regression: full country sample - egalitarian preferences index",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

>>>>

coefmap <-  list(homclass ="Class-based network homogeneity",
                 'class3Intermediate class (III+IV)' ='Intermediate Class',
                 'class3Working Class (V+VI+VII)' ='Working Class',
                 "Q03pcmT02" = "Middle",
                 "Q03pcmT03" = "High",
                 "edyears" = 'Education in years',
                 "workstNot in paid work"="Not in labor force",
                 "unionYes" = 'Union membership: Yes',
                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
                 )

htmlreg(
  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
  caption = "Multilevel linear regression: full country sample - egalitarian preferences index",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ), 
  custom.coef.map = coefmap
  )
```
